Space-time plots

### 2017-04-06 Rmd/space-time.Rmd
Plots revised through histogram (Figure 1).

# Space versus time analysis
```{r, message = FALSE, warning=FALSE, results='hold'}
library(ecoscales)
library(readxl)
library(stringdist)
library(maptools)
library(RColorBrewer)

p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data/result")
p_calib <- full_path(p_root, "external/data/calibration")
# dat <- as.data.table(read_excel(full_path(p_dat, "merged.xlsx")))
dat <- as.data.table(read_excel(full_path(p_dat, "mergedfffff.xlsx")))
dato <- as.data.table(read_excel(full_path(p_dat, "archive/mergedfff.xlsx")))
cal <- data.table(read_excel(fp(p_calib, "merged_calibrationfffff.xlsx")))
full <- data.table(read_excel(fp(p_dat, "full_no_treuer_toss.xlsx")))
# full <- data.table(read_excel(fp(p_dat, "full_less_Treuer.xlsx")))

setnames(dato, "DOI/title", "DOI")
dato[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dato[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace

setnames(dat, "DOI/title", "DOI")
dat[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dat[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
cal[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
full <- gsub("DOI:|doi:|DOI: |doi: |DOI ", "", full$DOI)
full <- gsub("\\s", "", full)  # remove DOI and whitespace

# subset main results and define study type
dat <- dat[, names(dat)[1:22], with = FALSE]
dat[, study_type := tolower(study_type)]
# kwords <- c("field", "paleo", "remote", "automated", "other")
tst <- dat[, study_type]

@@

kwords <- cbind(c("field", "direct", "paleo", "remote", "automated", "other"),
                c("field", "field", "paleo", "remote", "automated", "other"))
cal[, study_type := tolower(study_type)]
tst <- cal[, study_type]
for(i in 1:nrow(kwords)) {
  cal[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}
# cbind(tst, cal[, study_type])

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
# dat2 <- copy(dat[, .(st, DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
#                      samp_dur, t_btwn_samp, act_dur, eff_dur)])
# rnms <- c("st", "DOI", "study_type", "feature", "observer", "plot_res", 
#           "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
#           "act_dur", "eff_dur")
dat2 <- copy(dat[, .(DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
                     samp_dur, t_btwn_samp, act_dur, eff_dur)])
rnms <- c("DOI", "study_type", "feature", "observer", "plot_res", 
          "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
          "act_dur", "eff_dur")
calr <- cal[, rnms, with = FALSE]
selind <- c(3, 5:length(rnms))
for(j in names(calr)[selind]) set(calr, j=j, value = as.numeric(calr[[j]]))

@@

```{r, message=FALSE, warning=FALSE, results='hide'}
# apply fixes (mostly to account for observer omissions)
# 1. if samp_dur != act_dur and t_btwn_samp == 0, set 
#    act_dur == samp_dur
names(datf)
datf[t_btwn_samp == 0 & (act_dur != samp_dur), ]  
dat[t_btwn_samp == 0 & (act_dur != samp_dur), c(1, 3, 8:13), with=F]  
# function to set t_btwn_samp to 365 * 100000 to indicate once-off studies 
# when t_btwn_samp == 0.  
to_infin_byond <- function(tbtwn) ifelse(tbtwn == 0, 365 * 10000, tbtwn)

@@

```{r, eval=FALSE}
# p <- c(0.64, 0.84, 0.53, 1.21)  # from calibration.Rmd
p <- c(0.58, 0.82, 0.99, 1.24)  # from calibration.Rmd

# Function for bootstrapping with uncertainties
resamp_func <- function(dat, p, iter) {
  bout <- lapply(1:iter, function(x) {
    if((x / 100) %in% 1:100) print(x)
    if(length(p) < 4) stop("p must be length of 4", call. = FALSE)

    dnew <- copy(datf[, .(plot_res, act_ext, t_btwn_samp, act_dur)])
    # modifiers
    modvec <- sapply(p, function(y) {
      mv <- runif(nrow(dnew), min = 1 - y, max = 1 + y)
      mv
    })

    for(j in 1:ncol(modvec)) set(dnew, j = j, value = dnew[[j]] * modvec[, j])
    dnew[plot_res <= 0, plot_res := 0.00000001]
    dnew[act_ext <= 0, act_ext := 0.00000001]
    dnew[act_dur <= 0, act_dur := 0.00000001]
    dnew[t_btwn_samp < 0, t_btwn_samp := 0.00000001]

@@

set.seed(1)
bootperturb <- resamp_func(datf, p = p, iter = 1000)  # 10% perturb
# bootperturb2 <- resamp_func(datf, p = p, iter = 1000)  # 10% perturb
# all(bootperturb[[200]]$plot_res == bootperturb2[[200]]$plot_res)
# rm(bootperturb2)

@@

# sampled area
alab2 <- c(expression(paste(NULL<="0.1 m"^2)), expression("1 m"^2),
           expression("10 m"^2), 
           expression("100 m"^2), expression("1000 m"^2), expression("1 ha"),
           expression("10 ha"), expression("100 ha"), expression("1000 ha"), 
           expression(paste(10^4 , " ha")), expression(paste(10^5 , " ha")), 
           expression(paste(10^6 , " ha")), expression(paste(10^7 , " ha")), 
           expression(paste(10^8 , " ha")), expression(paste(10^9 , " ha")), 
           expression(paste(10^10 , " ha")))

aaxis2 <- cbind.data.frame(
  c(0.1 / 10000, 1 / 10000, 10 / 10000, 100 / 10000, 1000 / 10000, 1, 10, 10^2,
    10^3, 10^4, 10^5, 10^6, 10^7, 10^8, 10^9, 10^10))
aaxis2 <- data.table(aaxis2)
setnames(aaxis2, names(aaxis2), "area")
aaxis2[, logarea := log10(area)]

@@

```{r, eval=FALSE}
length(which(datf$study_type %in% 
               c("remote sensing", "other geographic data"))) / nrow(datf)
datf[t_btwn_samp == 0, .N] / datf[, .N]  # 36% of samples are once-offs
datf[act_dur == samp_dur, .N] / nrow(datf)
datf[(act_dur == samp_dur) & t_btwn_samp != 0]
datf[(act_dur != samp_dur) & t_btwn_samp == 0]

hdat <- cbind("res" = log10(datf$plot_res), "ext" = log10(datf$act_ext), 
              "int" = log10(to_infin_byond(datf$t_btwn_samp)), 
              "dur" = log10(datf$act_dur))
hdat <- data.table(hdat)
# set bounds for histograms
hdat[res < aaxis1$logres[1], res := aaxis1$logres[1]]
hdat[res > ry[2], res := ry[2]]
hdat[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)

# histograms from bootstrap
brksl <- list(aaxis1$logres, c(-6, aaxis2$logarea), taxis1$logdays,
              taxis2$logdays)

vs <- c("res", "ext", "int", "dur")
hdat_bs <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  print(x)
  DT <- bootperturb[[x]]
  hdb <- cbind("res" = log10(DT$plot_res), "ext" = log10(DT$act_ext), 
               "int" = log10(to_infin_byond(DT$t_btwn_samp)), 
               "dur" = log10(DT$act_dur))
  hdb <- data.table(hdb)
  hdb[res < aaxis1$logres[1], res := aaxis1$logres[1]]
  hdb[res > ry[2], res := ry[2]]
  hdb[, lapply(.SD, range)]
  hdb[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)
  hists <- lapply(1:length(vs), function(y) {  # y <- 2
    #print(y)
    hdbv <- hdb[[vs[y]]]
    hbrks <- brksl[[y]]
    hdbv[hdbv < hbrks[1]] <- hbrks[1]
    hdbv[hdbv > hbrks[length(hbrks)]] <- hbrks[length(hbrks)]
    h <- hist(hdbv, breaks = hbrks, plot = FALSE)
    h$density <- h$counts / sum(h$counts) * 100
    h
  })
})

@@

## Ordinary histograms
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- 35
# pdf("paper/figures/hists.pdf", width = 7, height = 2.5)
pdf("paper/figures/hists3.pdf", width = 5, height = 5)
par(mfrow = c(2, 2), mar = c(4.5, 1, 1, 1), oma = c(2, 3, 0, 0))
# resolution
h <- hist(hdat$res, breaks = aaxis1$logres, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial resolution", 
     ylim = c(0, yl - 10), main = "", col = reds[4], cex.lab = cxl)
axis(1, at = aaxis1$logres, labels = alab1, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)
mtext("A", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# extent
h <- hist(hdat$ext, breaks = c(-6, aaxis2$logarea), plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial extent", ylim = c(0, yl - 10), 
     main = "", col = reds[6], cex.lab = cxl)
axis(1, at = c(-6, aaxis2$logarea), 
     labels = c(expression(paste(NULL<="0.01m"^2)), expression(paste(0.1, m^2)),                 alab2[-1]), las = 2, cex.axis = cxa,
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("B", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# interval
tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$int, breaks = taxis1$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Sampling interval", ylim = c(0, yl), 
     main = "", col = blues[4], cex.lab = cxl)
axis(1, at = tax, labels = tlab1[-10], las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, -0.34))
mtext("C", side = 3, line = sfigl, cex = 0.8, adj = 0.05)
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)

# duration
# tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$dur, breaks = taxis2$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Temporal duration", ylim = c(0, yl), 
     main = "", col = blues[6], cex.lab = cxl)
axis(1, at = taxis2$logdays, labels = tlab2, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("D", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

@@

### Bootstrapped histograms (now main figure)
qtf <- function(x) c(mean(x), quantile(x, probs = c(0.025, 0.975))) # quant f
xlabs <- c("Spatial resolution", "Spatial extent", "Sampling interval", 
           "Temporal duration")
# axes <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
#              "tax1" = taxis1$logdays, "tax2" = taxis2$logdays)
axes2 <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
              "tax1" = c(taxis2$logdays[-c(10:11)],
                         mean(taxis2$logdays[c(10:11)])), 
              "tax2" = taxis2$logdays)
axlabs <- list(alab1, c(expression(paste(NULL<="0.01m"^2)),
                        expression(paste(0.1, m^2)), alab2[-1]),
               tlab1[-10], tlab2)
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
# plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- 35
cols <- c(reds[c(4, 6)], blues[c(4, 6)])

@@

    # base plot
  yl <- ifelse(i %in% c(1, 2), 30, 35) 
  plot(c(axv[1], axv[length(axv)]), c(0, yl - 10), ylab = "", las = 2, 
         xaxt = "n", xlab = xlabs[i], ylim = c(0, yl), main = "", 
         col = cols[i], cex.lab = cxl, pch = "", bty = "l", axes = FALSE)

@@

# stats
# bootp_dt
# axisl <- list(aaxis1$logres, c(-6, aaxis2$logarea), taxis1$logdays,
#               taxis2$logdays)
hdatstat <- lapply(1:4, function(x) {
  h <- hist(hdat[[x]], breaks = brksl[[x]], plot = FALSE)
  h$density <- h$counts / sum(h$counts) * 100
  h
})

@@

# extent
# hdatst <- hdatstat[[2]]$density
hdatst <- hdatstat_bt$ext$mu
l <- length(hdatst)
sum(hdatst[1:2])  # 36 % < 1 m^2
sum(hdatst[1:6])  # 82% < 1 ha
sum(hdatst[1:7])  # 86% < 10 ha
sum(hdatst[1:8])  # 90 % < 100 ha
sum(hdatst[1:9])  # 92 % < 1000 ha
sum(hdatst[8:9])  # 6 % 10-1000 ha
sum(hdatst[8:l])  # 14% > 10 ha
sum(hdatst[10:l]) # 8.2 % covered an area > 1000 ha
sum(hdatst[12:l]) # 5.1 % covered an area > 100,000 ha
sum(hdatst[13:l]) # 3.9 % covered an area > 1,000,000 ha

>>>>

# Space versus time analysis
```{r, message = FALSE, warning=FALSE, results='hold'}
library(ecoscales)
library(readxl)
# library(stringdist)
library(maptools)
library(RColorBrewer)

p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data/result")
p_calib <- full_path(p_root, "external/data/calibration")
# dat <- as.data.table(read_excel(full_path(p_dat, "merged.xlsx")))
dat <- as.data.table(read_excel(full_path(p_dat, "mergedfffff.xlsx")))
# dato <- as.data.table(read_excel(full_path(p_dat, "archive/mergedfff.xlsx")))
cal <- data.table(read_excel(fp(p_calib, "merged_calibrationfffff.xlsx")))
full <- data.table(read_excel(fp(p_dat, "full_no_treuer_toss.xlsx")))
# full <- data.table(read_excel(fp(p_dat, "full_less_Treuer.xlsx")))

# setnames(dato, "DOI/title", "DOI")
# dato[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
# dato[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace

# clean up DOIs
setnames(dat, "DOI/title", "DOI")
dat[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dat[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
cal[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
full <- gsub("DOI:|doi:|DOI: |doi: |DOI ", "", full$DOI)
full <- gsub("\\s", "", full)  # remove DOI and whitespace

# subset main results and define study type
dat <- dat[, names(dat)[1:22], with = FALSE]
dat[, study_type := tolower(study_type)]
# kwords <- c("field", "paleo", "remote", "automated", "other")
# tst <- dat[, study_type]

@@

kwords <- cbind(c("field", "direct", "paleo", "remote", "automated", "other"),
                c("field", "field", "paleo", "remote", "automated", "other"))
cal[, study_type := tolower(study_type)]
# tst <- cal[, study_type]
for(i in 1:nrow(kwords)) {
  cal[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}
# cbind(tst, cal[, study_type])

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
# dat2 <- copy(dat[, .(st, DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
#                      samp_dur, t_btwn_samp, act_dur, eff_dur)])
# rnms <- c("st", "DOI", "study_type", "feature", "observer", "plot_res", 
#           "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
#           "act_dur", "eff_dur")
dat2 <- copy(dat[, .(DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
                     samp_dur, t_btwn_samp, act_dur, eff_dur)])
selind <- 3:ncol(dat2)
for(j in names(dat2)[selind]) set(dat2, j=j, value = as.numeric(dat2[[j]]))
rnms <- c("DOI", "study_type", "feature", "observer", "plot_res", 
          "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
          "act_dur", "eff_dur")
calr <- cal[, rnms, with = FALSE]
selind <- c(3, 5:length(rnms))
for(j in names(calr)[selind]) set(calr, j=j, value = as.numeric(calr[[j]]))

@@

```{r, message=FALSE, warning=FALSE, results='hide'}
# apply fixes (mostly to account for observer omissions)
# 1. if samp_dur != act_dur and t_btwn_samp == 0, set 
#    act_dur == samp_dur
names(datf)
datf[t_btwn_samp == 0 & (act_dur != samp_dur), ]  
dat[t_btwn_samp == 0 & (act_dur != samp_dur), c(1, 3, 8:13), with = F]  
# function to set t_btwn_samp to 365 * 100000 to indicate once-off studies 
# when t_btwn_samp == 0.  
to_infin_byond <- function(tbtwn) ifelse(tbtwn == 0, 365 * 10000, tbtwn)

@@

```{r, eval=FALSE}
# p <- c(0.64, 0.84, 0.53, 1.21)  # from calibration.Rmd
# p <- c(0.58, 0.82, 0.99, 1.24)  # from calibration.Rmd
##     plot_res   n_sites   act_ext   eff_ext t_btwn_samp  act_dur   eff_dur
## 1: 0.5769693 0.3821107 0.7196559 0.4049972     1.01134 1.253045 0.5284913
p <- c(0.58, 0.72, 0.41, 1.01, 1.25, 0.53)  # from calibration.Rmd

# Function for bootstrapping with uncertainties
vars <- c("plot_res", "act_ext", "eff_ext", "t_btwn_samp", "act_dur", 
          "eff_dur")

resamp_func <- function(dat, vars, p, iter) {
  bout <- lapply(1:iter, function(x) {  # x <- 1
    if((x / 100) %in% 1:100) print(x)
    if(length(p) < length(var)) stop("p must be length of var", call. = FALSE)

    # dnew <- copy(datf[, .(plot_res, act_ext, eff_ext, t_btwn_samp, act_dur)])
    # dnew <- copy(datf[, vars, with = FALSE])
    dnew <- copy(dat[, vars, with = FALSE])
    # modifiers
    modvec <- sapply(p, function(y) {
      mv <- runif(nrow(dnew), min = 1 - y, max = 1 + y)
      mv
    })
    # plot(dnew[[j]] * modvec[, j], dnew[[j]])

    # perturb and set any values < 0 to very small amount
    for(j in 1:ncol(modvec)) set(dnew, j = j, value = dnew[[j]] * modvec[, j])
    dnew[plot_res <= 0, plot_res := 0.00000001]
    dnew[act_ext <= 0, act_ext := 0.00000001]
    dnew[eff_ext <= 0, eff_ext := 0.00000001]
    dnew[act_dur <= 0, act_dur := 0.00000001]
    dnew[eff_dur <= 0, eff_dur := 0.00000001]
    dnew[t_btwn_samp < 0, t_btwn_samp := 0.00000001]

@@

set.seed(1)
bootperturb <- resamp_func(datf, vars = vars, p = p, iter = 1000) # 10% perturb
# bootperturb2 <- resamp_func(datf, p = p, iter = 1000)  # 10% perturb
# all(bootperturb[[200]]$plot_res == bootperturb2[[200]]$plot_res)
# rm(bootperturb2)
```

```{r, echo = FALSE, eval=FALSE}
# check
par(mfrow = c(2, 3))
for(i in sample(1:1000, 6)) {
  plot(datf[, eff_ext], datf[, eff_ext] - bootperturb[[i]][, eff_ext], 
       pch = 20)
}
```

@@

# effective extent
### fix this here to have label for 10^-6 (so that limit isn't hard-coded below)
alab2 <- c(expression(paste(NULL<="0.1 m"^2)), expression("1 m"^2),
           expression("10 m"^2), 
           expression("100 m"^2), expression("1000 m"^2), expression("1 ha"),
           expression("10 ha"), expression("100 ha"), expression("1000 ha"), 
           expression(paste(10^4 , " ha")), expression(paste(10^5 , " ha")), 
           expression(paste(10^6 , " ha")), expression(paste(10^7 , " ha")), 
           expression(paste(10^8 , " ha")), expression(paste(10^9 , " ha")), 
           expression(paste(10^10 , " ha")))

### fix this here to have value for 10^-6 (so that limit isn't hard-coded below)
aaxis2 <- cbind.data.frame(
  c(0.1 / 10000, 1 / 10000, 10 / 10000, 100 / 10000, 1000 / 10000, 1, 10, 10^2,
    10^3, 10^4, 10^5, 10^6, 10^7, 10^8, 10^9, 10^10))
aaxis2 <- data.table(aaxis2)
setnames(aaxis2, names(aaxis2), "area")
aaxis2[, logarea := log10(area)]
```

@@

```{r, eval=FALSE}
# length(which(datf$study_type %in% c("remote", "other"))) / nrow(datf)
datf[t_btwn_samp == 0, .N] / datf[, .N]  # 38% of samples are once-offs
datf[act_dur == samp_dur, .N] / nrow(datf)
datf[(act_dur == samp_dur) & t_btwn_samp != 0]
datf[(act_dur != samp_dur) & t_btwn_samp == 0]

hdat <- cbind("res" = log10(datf$plot_res), "aext" = log10(datf$act_ext),
              "ext" = log10(datf$eff_ext), 
              "int" = log10(to_infin_byond(datf$t_btwn_samp)), 
              "adur" = log10(datf$act_dur), "dur" = log10(datf$eff_dur))
# NA data checks
# hdat[is.na(rowSums(hdat)), ]
# dat[DOI %in% datf[which(is.na(rowSums(hdat))), DOI], ]
# dat[DOI %in% datf[which(is.na(hdat[, 6])), DOI]]
# dat[DOI %in% datf[which(is.na(hdat[, 3])), DOI]]
# calr[DOI %in% datf[which(is.na(hdat[, 3])), DOI] & is.na(eff_ext)]

hdat <- data.table(hdat)

# set bounds for histograms
# first set variable limits
vlr <- range(aaxis1$logres)  #for resolution
### fix in scaling section (so that min extent limit isn't hard-coded)
vle <- c(-6, range(aaxis2$logarea)[2])  ### fix

# then apply limits to main (unperturbed) set of variables
hdat[res < vlr[1], res := vlr[1]]  # set min res to 0.01 cm"^2 
hdat[res > vlr[2], res := vlr[2]]  # set max res to 10000 ha 
hdat[ext < vle[1], ext := vle[1]]  # set minimum extent -6 (0.01 m2) 
hdat[ext > vle[2], ext := vle[2]]  # set maximum extent 10 (10^10 ha)
# hdat[aext < vle[1], aext := vle[1]]  # set minimum extent -6 (0.01 m2) 
# hdat[aext > vle[2], aext := vle[2]]  # set maximum extent 10 (10^10 ha)

# histograms from bootstrap
### fix in scaling section (so that min extent limit isn't hard-coded)
brksl <- list(aaxis1$logres, c(-6, aaxis2$logarea), taxis1$logdays,
              taxis2$logdays)

vs <- c("res", "ext", "int", "dur")
hdat_bs <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  print(x)
  DT <- bootperturb[[x]]
  hdb <- cbind("res" = log10(DT$plot_res), "ext" = log10(DT$eff_ext), 
               "int" = log10(to_infin_byond(DT$t_btwn_samp)), 
               "dur" = log10(DT$eff_dur))
  hdb <- data.table(hdb)
  hdb[res < vlr[1], res := vlr[1]]  # set min res to 0.01 cm"^2 
  hdb[res > vlr[2], res := vlr[2]]  # set max res to 10000 ha 
  # hdb[, lapply(.SD, range, na.rm = TRUE)]
  ### fix in scaling section (so that this limit isn't hard-coded)
  hdb[ext < vle[1], ext := vle[1]]  # set minimum extent -6 (0.01 m2)
  hdb[ext > vle[2], ext := vle[2]]  # set maximum extent 10 (10^10 ha)
  hists <- lapply(1:length(vs), function(y) {  # y <- 2
    #print(y)
    hdbv <- hdb[[vs[y]]]
    hbrks <- brksl[[y]]
    hdbv[hdbv < hbrks[1]] <- hbrks[1]
    hdbv[hdbv > hbrks[length(hbrks)]] <- hbrks[length(hbrks)]
    h <- hist(hdbv, breaks = hbrks, plot = FALSE)
    h$density <- h$counts / sum(h$counts) * 100
    h
  })
})

@@

## Ordinary histograms
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- c(25, 40)
# pdf("paper/figures/hists.pdf", width = 7, height = 2.5)
pdf("paper/figures/hists.pdf", width = 5, height = 5)
par(mfrow = c(2, 2), mar = c(4.5, 1, 1, 1), oma = c(2, 3, 0, 0))
# resolution
h <- hist(hdat$res, breaks = aaxis1$logres, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial resolution", 
     ylim = c(0, yl[1]), main = "", col = reds[4], cex.lab = cxl)
axis(1, at = aaxis1$logres, labels = alab1, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)
mtext("A", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# extent
### fix in scaling section (so that this limit isn't hard-coded)
h <- hist(hdat$ext, breaks = c(-6, aaxis2$logarea), plot = FALSE)
# h <- hist(hdat$aext, breaks = c(-6, aaxis2$logarea), plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Spatial extent", ylim = c(0, yl[1]), 
     main = "", col = reds[6], cex.lab = cxl)
### fix in scaling section (so that this limit isn't hard-coded)
axis(1, at = c(-6, aaxis2$logarea),  
     labels = c(expression(paste(NULL<="0.01m"^2)), expression(paste(0.1, m^2)),                 alab2[-1]), las = 2, cex.axis = cxa,
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("B", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

# interval
tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$int, breaks = taxis1$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Sampling interval", ylim = c(0, yl[2]), 
     main = "", col = blues[4], cex.lab = cxl)
axis(1, at = tax, labels = tlab1[-10], las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, -0.34))
mtext("C", side = 3, line = sfigl, cex = 0.8, adj = 0.05)
mtext("Percent of observations", side = 2, line = 1.5, cex = 0.8)

# duration
# tax <- c(taxis2$logdays[-c(10:11)], mean(taxis2$logdays[c(10:11)]))
h <- hist(hdat$dur, breaks = taxis2$logdays, plot = FALSE)
h$density <- h$counts / sum(h$counts) * 100
plot(h, freq = FALSE, ylab = "", las = 2,  xaxt = "n", mgp = c(3.25, 0.25, mga),
     tcl = -0.2, cex.axis = cxa, xlab = "Temporal duration", ylim = c(0, yl[2]), 
     main = "", col = blues[6], cex.lab = cxl)
axis(1, at = taxis2$logdays, labels = tlab2, las = 2, cex.axis = cxa, 
     tcl = -0.2, mgp = c(2, 0.25, mga))
mtext("D", side = 3, line = sfigl, cex = 0.8, adj = 0.05)

@@

### Bootstrapped histograms (now main figure)
qtf <- function(x) c(mean(x), quantile(x, probs = c(0.025, 0.975))) # quant f
xlabs <- c("Spatial resolution", "Spatial extent", "Sampling interval", 
           "Temporal duration")
# axes <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
#              "tax1" = taxis1$logdays, "tax2" = taxis2$logdays)
### fix in scaling section (so that this limit isn't hard-coded)
axes2 <- list("aax1" = aaxis1$logres, "aax2" = c(-6, aaxis2$logarea), 
              "tax1" = c(taxis2$logdays[-c(10:11)],
                         mean(taxis2$logdays[c(10:11)])), 
              "tax2" = taxis2$logdays)
### fix in scaling section (so that this limit isn't hard-coded)
axlabs <- list(alab1, c(expression(paste(NULL<="0.01m"^2)),
                        expression(paste(0.1, m^2)), alab2[-1]),
               tlab1[-10], tlab2)
mga <- -0.34
sfigl <- -1.2
cxa <- 0.8
cxl <- 0.9
reds <- brewer.pal(9, name = "Reds")
blues <- brewer.pal(9, name = "Blues")
# plot(1:2, pch = 20, col = blues[c(4, 6)])
yl <- 35
cols <- c(reds[c(4, 6)], blues[c(4, 6)])

@@

    # base plot
  yl <- ifelse(i %in% c(1, 2), 25, 40) 
  plot(c(axv[1], axv[length(axv)]), c(0, yl), ylab = "", las = 2, 
         xaxt = "n", xlab = xlabs[i], ylim = c(0, yl), main = "", 
         col = cols[i], cex.lab = cxl, pch = "", bty = "l", axes = FALSE)

@@

# stats
# bootp_dt
# axisl <- list(aaxis1$logres, c(-6, aaxis2$logarea), taxis1$logdays,
#               taxis2$logdays)
# hdatstat <- lapply(1:4, function(x) {
#   h <- hist(hdat[[x]], breaks = brksl[[x]], plot = FALSE)
#   h$density <- h$counts / sum(h$counts) * 100
#   h
# })

@@

##############
# Ended here 6/4/2017 
##############
# extent
# hdatst <- hdatstat[[2]]$density
hdatst <- hdatstat_bt$ext$mu
l <- length(hdatst)
sum(hdatst[1:2])  # 36 % < 1 m^2
sum(hdatst[1:6])  # 82% < 1 ha
sum(hdatst[1:7])  # 86% < 10 ha
sum(hdatst[1:8])  # 90 % < 100 ha
sum(hdatst[1:9])  # 92 % < 1000 ha
sum(hdatst[8:9])  # 6 % 10-1000 ha
sum(hdatst[8:l])  # 14% > 10 ha
sum(hdatst[10:l]) # 8.2 % covered an area > 1000 ha
sum(hdatst[12:l]) # 5.1 % covered an area > 100,000 ha
sum(hdatst[13:l]) # 3.9 % covered an area > 1,000,000 ha
